### 2021-04-22 README.Rmd
sdaf

The second option is tailored for those interested users with no awareness of LaTeX. `{steveproj}` imports `{rmarkdown}`, which in turn imports `{tinytex}`. This would install and maintain a version of LaTeX to compile these documents that ostensibly precludes the need to install the more comprehensive suites available for download and installation on the internet. I will only add that users who do this should know the preferred flavor of LaTeX template (from `{stevetemplates}`) in this package requires one additional LaTeX dependency that `{tinytex}` does not install by default. You may encounter a vague error in rendering to PDF that reads something like this.

>>>>

The second option is tailored for those interested users with no awareness of LaTeX. `{steveproj}` imports `{rmarkdown}`, which in turn imports `{tinytex}`. This would be an R package to install and maintain a version of LaTeX to compile these documents that ostensibly precludes the need to download the more comprehensive suites available on the internet as proper LaTeX distributions for different operating systems. Once `{tinytex}` is installed as an R package, this simple function will install a working version of LaTeX.

```r
tinytex::install_tinytex()
```

I will only add that users who do this should know the preferred flavor of LaTeX template (from `{stevetemplates}`) in this package requires one additional LaTeX dependency that `{tinytex}` does not install by default. You may encounter a vague error in rendering to PDF that reads something like this.
